A Comparison of Dimensionality Reduction Techniques for Robotic Motion Planning

### 2016-05-11 paper/paper.tex

\newcommand{\xr}[0]{\ensuremath{{x_{\Var{rand}}}}}
\newcommand{\xnear}[0]{\ensuremath{{x_{\Var{near}}}}}
\newcommand{\xnearest}[0]{\ensuremath{{x_{\Var{nearest}}}}}
\newcommand{\xnew}[0]{\ensuremath{{x_{\Var{new}}}}}
\newcommand{\xmin}[0]{\ensuremath{{x_{\Var{min}}}}}
\newcommand{\cmin}[0]{\ensuremath{{c_{\Var{min}}}}}
\newcommand{\cost}[0]{\ensuremath{{\Function{Cost}}}}
\newcommand{\linef}[1]{\ensuremath{{c(\Function{Line}(#1))}}}

@@

[RRT* algorithm]
[PRM* algorithm]

We used RRT* and PRM* in our project. The * indicates that these are the
asymptotically optimal versions of RRT and PRM (they are guaranteed to find the
optimal path as time goes to infinity). [Description of how RRT* and PRM* work]

@@

        \STATE $V \leftarrow \{x_{\Var{init}}\}$
        \STATE $E \leftarrow \emptyset$
        \FOR{$i = 1 \ \TO \ n$}
            \STATE $\xr \leftarrow \Var{SampleFree}_i$
            \STATE $\xnearest \leftarrow \Function{Nearest}(G = (V, E), \xr)$
            \STATE $\xnew \leftarrow \Function{Steer}(\xnearest, \xr)$
            \IF{$\Function{ObstacleFree}(\xnearest, \xnew)$}
                \STATE $\xnear \leftarrow \Function{Near}(G = (V, E), \xnew,
                \min \{\gamma \cdot \Function{RRT}(\log(|V|) / |V|)^{1 / d}, \eta\})$
                \STATE $V \leftarrow V \cup \{\xnew\}$
                \STATE $\xmin \leftarrow \xnearest$
                \STATE $\cmin \leftarrow \Function{Cost}(\xnear) +
                c(\Function{Line}(\xnearest, \xnew))$
                \FORALL{$\xnear \in X_{\Var{near}}$}
                    \STATE $C \leftarrow \cost(\xnear) + \linef{\xnear, \xnew}$
                    \IF{$\Function{CollisionFree}(\xnear, \xnew) \wedge C < \cmin$}
                        \STATE $\xmin \leftarrow \xnear$
                        \STATE $\cmin \leftarrow C$
                    \ENDIF
                    \STATE $E \leftarrow E \cup \{(\xmin, \xnew)\}$
                \ENDFOR
            \ENDIF
        \ENDFOR
        \RETURN $G = (V, E)$

>>>>

\newcommand{\xr}[0]{\ensuremath{{x_{\Var{rand}}}}}
\newcommand{\xnear}[0]{\ensuremath{{x_{\Var{near}}}}}
\newcommand{\xnearest}[0]{\ensuremath{{x_{\Var{nearest}}}}}
\newcommand{\xnew}[0]{\ensuremath{{x_{\Var{new}}}}}
\newcommand{\xmin}[0]{\ensuremath{{x_{\Var{min}}}}}
\newcommand{\xparent}[0]{\ensuremath{{x_{\Var{parent}}}}}
\newcommand{\cmin}[0]{\ensuremath{{c_{\Var{min}}}}}
\newcommand{\cost}[0]{\ensuremath{{\Function{Cost}}}}
\newcommand{\linef}[1]{\ensuremath{{c(\Function{Line}(#1))}}}

@@

We used RRT* and PRM* in our project. The * indicates that these are the
asymptotically optimal versions of RRT and PRM (they are guaranteed to find the
optimal path as time goes to infinity).

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in which a roadmap is constructed by sampling random points in the C-space, and the query phase in which a graph search over the roadmap is made to connect initial and goal configurations.The map is constructed during the preprocessing phase by sampling random points in the C-space and then adding them to the vertices in the roadmap within a certain radius of the point. PRM can be elevated to the asymptotically optimal PRM* by defining the radius to be a function of the number of vertices and the dimensionality of the space.

The Rapidly-expanding Random Tree algorithm works by building up a tree from the initial configuration to the goal configuration. Starting at the initial configuration as the root, it incrementally attempts to add randomly selected samples to the tree until it reaches the goal configuration. RRT* differs from RRT in that whenever a new node is added to the tree, connections are also tested to the new node from every other node that is within a certain radius from the new node. The the tree is pruned so that edges that are not part of the shortest path from the root of the tree to the new node are removed.

@@

        \STATE $V \leftarrow \{x_{\Var{init}}\}$
        \STATE $E \leftarrow \emptyset$
        \FOR{$i = 1 \ \TO \ n$}
            \STATE $\xr \leftarrow \Var{SampleFree}_i$
            \STATE $\xnearest \leftarrow \Function{Nearest}(G = (V, E), \xr)$
            \STATE $\xnew \leftarrow \Function{Steer}(\xnearest, \xr)$
            \IF{$\Function{ObstacleFree}(\xnearest, \xnew)$}
                \STATE $\xnear \leftarrow \Function{Near}(G = (V, E), \xnew,
                \min \{\gamma \cdot \Function{RRT}(\log(|V|) / |V|)^{1 / d}, \eta\})$
                \STATE $V \leftarrow V \cup \{\xnew\}$
                \STATE $\xmin \leftarrow \xnearest$
                \STATE $\cmin \leftarrow \Function{Cost}(\xnear) +
                c(\Function{Line}(\xnearest, \xnew))$
                \FORALL{$\xnear \in X_{\Var{near}}$}
                    \STATE $C \leftarrow \cost(\xnear) + \linef{\xnear, \xnew}$
                    \IF{$\Function{CollisionFree}(\xnear, \xnew) \wedge C < \cmin$}
                        \STATE $\xmin \leftarrow \xnear$
                        \STATE $\cmin \leftarrow C$
                    \ENDIF
                    \STATE $E \leftarrow E \cup \{(\xmin, \xnew)\}$
                \ENDFOR
                \FORALL{$\xnear \in X_{\Var{near}}$}
                    \STATE $C \leftarrow \cost(\xnew) + \linef{\xnew, \xnear}$
                    \IF{$\Function{CollisionFree}(\xnew, \xnear) \wedge C < \cost(\xnear)$}
                        \STATE $\xparent \leftarrow \Function{Parent}(\xnear)$
                        \STATE $E \leftarrow (E \backslash \{(\xparent, \xnear)\}) \cup \{(\xnew, \xnear)\}$
                    \ENDIF
                \ENDFOR
            \ENDIF
        \ENDFOR
        \RETURN $G = (V, E)$
